---
title: "R Graphics Tutorial"
author: Senthil Ramalingam
date: "July 28, 2015"
output: html_document
---

This is an R Graphics tutorial document explained by Mr.Guy Yollin.You can find his lecture notes at <http://faculty.washington.edu/gyollin/AMATH463.php>.

I just recreating his lecture notes to learn R. 

```{r load_required_libs,message=FALSE, warning=FALSE}
library(Ecdat)
library(dplyr)
library(xts)
library(quantmod)
library(TTR)
library(lubridate)
data("Capm")
```

# plot function <sup>is a generic function to plot an R object</sup>


## plot "risk free return" in points
```{r plot_points_rf}
plot(Capm$rf)
```

## plot "risk free return" in lines
```{r plot_lines_rf}
plot(Capm$rf, type = "l")
```

## plot "excess returns market portfolio" in bars
```{r plot_bars_rmrf}
plot(Capm$rmrf, type = "h")
```
## plotXY with "rmrf" and "excess returns construction industry"
```{r xy_plot_bars_rmrf}
plot(Capm$rmrf, Capm$rcon)
```

## plotting a blank frame
```{r plot_blank}
plot(0, xlim=c(-20,20), ylim=c(-20,20), type="n", xlab="market return", ylab="construction return")
```

## Adding points, lines and text on the above blank frame
#```{r plot_point_line_text}
points(x=Capm$rmrf, y= Capm$rcon, col="gray")
regression1= lm(Capm$rmrf ~ Capm$rcon)
abline(regression1, col="green")
regression2= lm(Capm$rcon ~ Capm$rmrf)
abline(regression2, col="blue")
lines(x=c(-20,20), y=c(-20,20), lwd=2, col="darkred")
text(20,20, labels="slope = 1", pos = 2)
#```
## R Graphics with par
```{r names_par}
names(par())
```

## Bar Plot
```{r bar_plot}
fromdate <- ymd("2015-01-01")
todate <-  ymd(Sys.Date())
msft <-getSymbols("MSFT",src="yahoo", from=fromdate, to=todate)
msft.returns <- periodReturn(MSFT,period = "monthly")
barplot(msft.returns,col="blue", names.arg = months(index(msft.returns)))
```






